---
title: "Exploring and Tagging Text"
author: "Ruxin Liu"
date: "11/17/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

# Introduction:
 
  In this assignment, we used the tnum package to explore and tag text from Pride
  and Prejudice by Jane Austen.
  
  
```{r}
# Install the package
# devtools::install_github("truenumbers/tnum/tnum")
library(tnum)
# Get access to the database
tnum.authorize()
```

```{r}
# Explore the text in the Pride and Prejudice
tax1 <-tnum.getDatabasePhraseList("subject", levels = 3)
tax1
```

```{r}
num1 <- tnum.query("*pride* has count:word")
num2 <- tnum.query("*pride* has text")
```


# Tag: love

  Since Pride and Prejudice is a romantic novel, the first word coming to my mind is love, and therefore, the love tag is added. It turns out that the word "love" has appeared in the book 111 times. 

  Below we showed a phrase graph by using tnum package.
  
```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"love\")", "reference:love")
love <- tnum.query("*pride* has text = REGEXP(\"love\")", max = 150) 
love_df <- tnum.objectsToDf(love)
# View(love_df)
piclove <- tnum.makePhraseGraphFromPathList(love_df$subject)
tnum.plotGraph(piclove)
```

## Creating Functions For Chapter Number


```{r}
ch_num <- function(query) {
  n <- length(query)
  vector <- rep(0, n)
  for(i in 1 : n) {
    vector[i] <- as.numeric(substring(str_split(tnum.getAttrFromList(query[i], "subject"), "[:/]")[[1]][4], 9))
  }
  return(vector)
}
```



## Creating Functions For Paragraph Number

```{r}
para_num <- function(query) {
  n <- length(query)
  vector <- rep(0, n)
  for(i in 1 : n) {
    vector[i] <- as.numeric(substring(str_split(tnum.getAttrFromList(query[i], "subject"), "[:/]")[[1]][5], 11))
  }
  return(vector)
}
```


  We also showed a distribution plot by using ggplot package, which presents the appearance frequency of the word "love" in different chapters and paragraphs. And it is interesting but not surprising to see that the word "love" occurs relatively more often towards the end, where the story is approaching the happy ending. 
  
```{r}
love_data <- data.frame(ch = ch_num(love), para = para_num(love))
ggplot(love_data, aes(ch)) +
  geom_histogram(aes(fill = as.factor(para)), binwidth = 1)+
  labs(title = "Distribution of The Word Love")+
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Paragraph Number") +
  xlab("Chapter Number")
```


# Tag: marry

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"marry\")", "reference:marry")
marry <- tnum.query("*pride* has text = REGEXP(\"marry\")", max = 60) 
marry_df <- tnum.objectsToDf(marry)
View(marry_df)
picmarry <- tnum.makePhraseGraphFromPathList(marry_df$subject)
tnum.plotGraph(picmarry)
```

# Three major male characters: Darcy, Bingley & Wickhamn

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Darcy\")", "reference:Darcy")
Darcy <- tnum.query("*pride* has text = REGEXP(\"Darcy\")", max = 400) 
```

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Bingley\")", "reference:Bingley")
Bingley <- tnum.query("*pride* has text = REGEXP(\"Bingley\")", max = 310) 
```

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Wickham\")", "reference:Wickham")
Wickham <- tnum.query("*pride* has text = REGEXP(\"Wickham\")", max = 190) 
```

```{r}
Darcy_n <- ch_num(Darcy)
Bingley_n <- ch_num(Bingley)
Wickham_n <- ch_num(Wickham)
```

```{r}
Darcy_table <- as.data.frame(table(Darcy_n))
Bingley_table <- as.data.frame(table(Bingley_n))
Wickham_table <- as.data.frame(table(Wickham_n))
```


```{r}
ggplot() +
  geom_path(data = Darcy_table, aes(x= as.numeric(Darcy_n), y = as.numeric(Freq), color = "red")) +
  geom_point(data = Darcy_table, aes(x= as.numeric(Darcy_n), y = as.numeric(Freq), color = "red")) +
  geom_path(data = Bingley_table, aes(x= as.numeric(Bingley_n), y = as.numeric(Freq), color = "blue")) +
  geom_point(data = Bingley_table, aes(x= as.numeric(Bingley_n), y = as.numeric(Freq), color = "blue")) +
  geom_path(data = Wickham_table, aes(x= as.numeric(Wickham_n), y = as.numeric(Freq), color = "green")) +
  geom_point(data = Wickham_table, aes(x= as.numeric(Wickham_n), y = as.numeric(Freq), color = "green")) +
  scale_color_discrete(name = "Character Name", labels = c("Bingley", "Wickham",  "Darcy")) +
  labs(x = "Chapter Number", y = "Frequency")
```




